Introductory statistics with `intRo`

### 2016-02-19 jcgs-paper-2016/paper.Rmd
More texttt

---
title: "Introductory statistics with `intRo`"
author:
  - name: Eric Hare
    affiliation: Iowa State University
    department: Department of Statistics
  - name: Andee Kaplan
    affiliation: Iowa State University
    department: Department of Statistics
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: preamble.tex
    number_sections: yes
    template: jcgs_article.tex
fontsize: 12pt
abstract: |
  `intRo` is a web-based application for performing basic data analysis and statistical routines. Leveraging the power of `R` and `Shiny`, `intRo` implements common statistical functions in an extensible modular structure, while including a point-and-click interface for the novice statistician. This simplicity lends itself to a natural presentation in an introductory statistics course as a substitute for other commonly used statistical software packages, such as `Excel` and `JMP`. `intRo` is currently deployed at the URL \url{http://www.intro-stats.com}. Within this paper, we introduce the application and explore the design decisions underlying `intRo`, as well as highlight some challenges and advantages of reactive programming.
keywords: Graphical User Interface, Interactivity, Reproducibility, Reactive Programming, Statistical Software, Programming Paradigms
bibliography: refs.bib
blind: false
---

@@

## `intRo` Package

@@

>>>>

---
title: "Introductory statistics with `intRo`"
author:
  - name: Eric Hare
    affiliation: Iowa State University
    department: Department of Statistics
  - name: Andee Kaplan
    affiliation: Iowa State University
    department: Department of Statistics
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: preamble.tex
    number_sections: yes
    template: jcgs_article.tex
fontsize: 12pt
abstract: |
  `intRo` is a web-based application for performing basic data analysis and statistical routines. Leveraging the power of R and Shiny, `intRo` implements common statistical functions in an extensible modular structure, while including a point-and-click interface for the novice statistician. This simplicity lends itself to a natural presentation in an introductory statistics course as a substitute for other commonly used statistical software packages, such as Excel and JMP. `intRo` is currently deployed at the URL \url{http://www.intro-stats.com}. Within this paper, we introduce the application and explore the design decisions underlying `intRo`, as well as highlight some challenges and advantages of reactive programming.
keywords: Graphical User Interface, Interactivity, Programming Paradigms, Reactive Programming, Reproducibility, Statistical Software
bibliography: refs.bib
blind: false
---

@@

## `intRo` package

@@

# Supplementary material
All code and documents related to this manuscript are available at \url{https://github.com/gammarama/intRo}.
